---
title: 'Exercise #3'
author: "Bichmai Vu (12057445), Nele Steiner (12548686)"
date: '`r Sys.Date()`'
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
---

    
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `exeRcise-sheet-3`. If you forgot how to do this, you can follow
    this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

d)  Name 2 strengths and 2 weaknesses of git.
    
strengths: 
1. It's very hard to lose files with git
2. Git allows easy collaboration as it allows everyone who is working on a project to see the changes other persons did
    
weaknesses: 
1. Git struggles with large files and a bit
2. Git needs to be used explicitly. It doesn`t just work in the background. 
    
e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below: <https://github.com/bichmaivu/exeRcise-sheet-3.git>
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (4.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2022` and
`2021`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.
    
```{r setup, include=FALSE}
library(tidyverse)
library(distill)
```

```{r}
vornamen_2022 <- read.csv("data/open_data_portal_2022.csv")
vornamen_2021 <- read.csv("data/vornamen_2021.csv")

vornamen_2021 <- vornamen_2021 %>% 
  rename(first_name = Vorname,
         number = Anzahl,
         gender = Geschlecht
    )

vornamen_2022 <- vornamen_2022 %>% 
  rename(first_name = Vorname,
         number = Anzahl,
         gender = Geschlecht
    )

typeof(vornamen_2021$number)
typeof(vornamen_2022$number)

vornamen_2021[vornamen_2021=="4 oder weniger"] <- "4"
vornamen_2022[vornamen_2022=="4 oder weniger"] <- "4"

vornamen_2021$number = as.numeric(vornamen_2021$number)
is.numeric(vornamen_2021$number)

vornamen_2022$number = as.numeric(vornamen_2022$number)
is.numeric(vornamen_2022$number)
```

The count variable ("number") has the type "character" in both years
because sometimes it's not sure how often a name get used, so it has an
explanation. This is the reason why the type of count variable isn't
right.

The repercussion is that the count variable "number" isn't exactly at it was in the beginning, because it was unsecure, if there were four babies or less that get that name.

The columns got renamed, so that everything is in one language (English).

c)  Calculate the total number of babies born in Munich in 2022
    and 2021. Which year had the bigger baby-boom?
    
```{r}
total_number_of_babies_2021 <- sum(vornamen_2021$number)

total_number_of_babies_2022 <- sum(vornamen_2022$number)

total_number_of_babies_2021
total_number_of_babies_2022
```

d)  Add a new column `year` to both datasets which holds the correct
    year for each.
    
```{r}
vornamen_2021 <- vornamen_2021 %>%
        mutate(year = 2021)
vornamen_2022 <- vornamen_2022 %>%
        mutate(year = 2022)
```

e)  Combine both datasets into one using `bind_rows()`.

```{r}
combination_2021_2022 <- bind_rows(vornamen_2021, vornamen_2022)
```

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
    
```{r}
most_popular_names <- combination_2021_2022 %>% 
  group_by(first_name) %>%
  summarise(total_number = sum(number)) %>%
  arrange(desc(total_number)) %>%
  head(10)

knitr::kable (most_popular_names, caption = "The top 10 names") 
```

## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.

###Create a sample data frame

tax_data \<- data.frame( 
Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"), 
Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), 
Tax_2021 = c(5200, 3800, 5900, 3400) 
)

###Calculate column-wise means

column_means \<- lapply(tax_data\[, -1\], 2, mean)

column_means

```{r}
# Corrected code by chat gbt
# Create a sample data frame

tax_data <- data.frame(
  Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
  Tax_2019 = c(5000, 4000, 6000, 3500),
  Tax_2020 = c(4800, 4200, 5800, 3700),
  Tax_2021 = c(5200, 3800, 5900, 3400)
)

column_means <- colMeans(tax_data[, -1])
column_means
```

There were two issues in the original code: 
1. The assignment operator "<-" was incorrectly written as "\<-". The correct operator is "<-", which is used for assigning values to variables in R.
2. The "lapply" function call had incorrect arguments. The code wasn't correct, because of presentation "\[, -1\]" and we need to correct this into "[, -1]". Also instead of 2, as the second argument need to pass the mean function. So the correct call should be "lapply(tax_data[, -1], mean)".


b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words. 

Explanation: The "rapply" function applies a function to each element of a list or nested list structure, and the "rapply" function traverses the structure recursively of "lapply", applying the function to all levels of nesting.

```{r}
my_list <- list(a = 1:3, b = 4:6, c = 7:9)

rapply(my_list, function(x) x^2)
```

Explanation: In this example "rapply" is used to take each value of "my_list" to square.

## Final Note

Make sure to push all your commits and changes to GitHub before
submitting the exercise sheet.
